\begin{enumerate}
    \item Immediate Inspection Physical Environment
          \begin{enumerate}
              \item Physical constraints
                    \begin{itemize}
                        \item Access for camera, lens, and lighting in 3-D space (working volume)
                        \item The size and shape of the working volume
                        \item Min and max camera, lighting working distance and field-of-view
                    \end{itemize}
              \item Part characteristics
                    \begin{itemize}
                        \item Sample stationary, moving, or indexed?
                        \item If moving or indexed, speeds, feeds, and expected cycle time?
                        \item Strobing? Expected pulse rate, on-time, and duty cycle?
                        \item Are there any continuous or shock vibrations?
                        \item Is the part presented consistently in orientation and position?
                        \item Any potential for ambient light contamination?
                    \end{itemize}
              \item Ergonomics and safety
                    \begin{itemize}
                        \item Man-in-the-loop for operator interaction?
                        \item Safety related to strobing or intense lighting applications?
                    \end{itemize}
          \end{enumerate}
    \item Sample - Light interactions
          \begin{enumerate}
              \item Sample Surface
                    \begin{itemize}
                        \item Reflectivity - Diffuse, specular, or mixed?
                        \item Overall Geometry - Flat, curved, or mixed?
                        \item Texture - Smooth, polished, rough, irregular, multiple?
                        \item Topography – Flat, multiple elevations, angles?
                        \item Light Intensity needed?
                    \end{itemize}
              \item Composition and Color
                    \begin{itemize}
                        \item Metallic, non-metallic, mixed, polymer?
                        \item Part color vs. background color
                        \item Transparent, semi-transparent, or opaque – IR transmission?
                        \item UV dye, or fluorescent polymer?
                    \end{itemize}
              \item Light Contamination
                    \begin{itemize}
                        \item Ambient contribution from overhead or operator station lighting?
                        \item Light contamination from another inspection station?
                        \item Light contamination from the same inspection station?
                    \end{itemize}
          \end{enumerate}
\end{enumerate}
